The Dark Matter Distribution of the Local Group inferred from Cosmological Simulations: I. The Halo Masses of M31, M33 and the Milky Way

### 2014-12-23 doc/ms1.tex
Update ms1.tex

\author{Philip J. Marshall\altaffilmark{1}}
\author{Marc Williamson\altaffilmark{1}}
\author{Michael T. Busha\altaffilmark{2}} 
\author{Risa H. Wechsler\altaffilmark{1}}
\author{Peter Behroozi\altaffilmark{3}}
\author{XX\altaffilmark{4}}
\author{YY\altaffilmark{5}}
\altaffiltext{1}{Kavli Institute for Particle Astrophysics and Cosmology, Stanford, CA, 94305, USA
{\tt pjm@slac.stanford.edu, rwechsler@stanford.edu}}
\altaffiltext{2}{???}
\altaffiltext{3}{STScI}
\altaffiltext{4}{YY}

@@

>>>>

\author{Philip J. Marshall\altaffilmark{1}}
\author{Marc Williamson\altaffilmark{1}}
\author{Michael T. Busha\altaffilmark{2}} 
\author{Risa H. Wechsler\altaffilmark{1}}
\author{XX\altaffilmark{3}}
\author{YY\altaffilmark{4}}
\altaffiltext{1}{Kavli Institute for Particle Astrophysics and Cosmology, Stanford, CA, 94305, USA
{\tt pjm@slac.stanford.edu, rwechsler@stanford.edu}}
\altaffiltext{2}{???}
\altaffiltext{3}{XX}
\altaffiltext{4}{YY}

@@

We use the observed distances and radial and tangential velocities of the MW and M33 in Table 1 to construct a probability density function for the Local Group. Assuming that the values in the table come from Gaussian distributions, we sample a large number of systems similar to the Local Group.

The density of this "observational" dataset is fit well by a Gaussian mixture model (GMM). (Plot showing goodness of fit? Triangular plot?) The optimal number of components in the GMM is found using the Bayesian Information Criterion with cross validation. The GMM allows us to evaluate the likelihood of a Consuelo Local Group under the observational pdf. This likelihood is an importance weight which allows us to find marginalized posterior pdf's for the Consuelo halo properties.
